>

### 2019-10-03 04_estimation.Rmd
Add discussion of SLX vs SDEM tests

```{r visual_compare}
lapply(slx_vs_sdem, tidy) %>%
  bind_rows(.id = "model") %>%
  dwplot() + scale_x_continuous(limits = c(-0.5, 0.5))
lapply(slx_vs_sdem, tidy) %>%
  bind_rows(.id = "model") %>%
  dwplot() 
```

>>>>

```{r visual_compare}
lapply(slx_vs_sdem, tidy) %>%
  bind_rows(.id = "model") %>%
  dwplot() + scale_x_continuous(limits = c(-0.5, 0.6))
lapply(slx_vs_sdem, tidy) %>%
  bind_rows(.id = "model") %>%
  dwplot() 
```

### 2019-10-03 manuscript/manuscript.Rmd
Add discussion of SLX vs SDEM tests

options(tigris_use_cache = TRUE)
opts_chunk$set(cache=TRUE, message = FALSE, echo = FALSE, warning = FALSE)
library(leaflet)

@@

For comparative purposes, we also employ an isochrone analysis using the
10-minute walk threshold calculated for ParkScore [@parkscore2019]. If the
population-weighted centroid of a tract is within a 10-minute walk of a green space
as defined by ParkScore, the tract is considered as having "access" to a park.
The centroid is necessary as all tracts in New York City have at least *some* 
intersection with the 10-minute walk buffer; as it is, only 
`r sum(!tracts$walk_10)` of the `r nrow(tracts)` tract centroids are not located 
in this buffer.

@@

As the observations are related to each other spatially, it is likely that this
process involves spatial spillovers of one kind or another. A complete treatment of
spatial econometrics is not warranted here; the reader is directed to
@LeSage2009 as well as @LeSage2014.
Suffice it to say that the presence of spatial data generating processes can
negatively affect econometric interpretation in a variety of ways. Each of these
process relies on spatial autoregression, where elements of some random
variable $x$ are spatially dependent on other elements, 
\begin{equation}\label{eq:autoregression}
 x = \rho W x + \varepsilon
\end{equation}
with the strength of dependence an estimated parameter $\rho$, the structure of 
dependence governed by the asserted matrix $W$ (details of $W$ follow below),
and some random uncorrelated residual $\varepsilon$. A collection of models is
available to represent spatial autodependence in the model residuals, the 
independent variables, and the dependent variable.

@@

names_for_terms <- c(
  base_termnames, str_c("$\\gamma$: ", base_termnames[-1]),
  "$\\lambda$: spatial correlation"
)

access_terms <- c("Logsum", "Tweets",  "Attributes", "10-min walk")
```

>>>>

options(tigris_use_cache = TRUE)
opts_chunk$set(cache=FALSE, message = FALSE, echo = FALSE, warning = FALSE)
library(leaflet)

@@

For comparative purposes, we also employ an isochrone analysis using the
10-minute walk threshold calculated for ParkScore [@parkscore2019]. If the
population-weighted centroid of a tract is within a 10-minute walk of a green space
as defined by ParkScore, the tract is considered as having "access" to a park.
The centroid is necessary as all tracts in New York City have at least *some* 
intersection with the 10-minute walk buffer; as it is, only 
`r sum(!tracts$walk_10)` of the `r nrow(tracts)` tract centroids are not located 
within this buffer.

@@

As the observations are related to each other spatially, it is likely that this
process involves spatial spillovers of one kind or another. A complete treatment of
spatial econometrics is not warranted here; the reader is directed to
@LeSage2009 as well as @LeSage2014.
Suffice it to say that the presence of spatial data generating processes can
negatively affect econometric interpretation in a variety of ways. Each of these
process relies on spatial autoregression, where elements of some random
variable $x$ are spatially dependent on other elements, 
\begin{equation}\label{eq:autoregression}
 x = \rho W x + \varepsilon
\end{equation}
with the strength of dependence an estimated parameter $\rho$, the structure of 
spatial dependence governed by the asserted matrix $W$ (details of $W$ follow below),
and some random uncorrelated residual $\varepsilon$. A collection of models is
available to represent spatial autodependence in the model residuals, the 
independent variables, and the dependent variable.

@@

names_for_terms <- c(
  base_termnames, str_c("$\\gamma$: ", base_termnames[-1])
)

lambda <- "$\\lambda$: spatial correlation"
access_terms <- c("Logsum", "Tweets",  "Attributes", "10-min walk")
```

```{r slx_hausman}
slx_hausman <- function(slx, sdem) {
  b1 <- slx$coefficients
  b2 <- sdem$coefficients
  db <- b1 - b2

  V1 <- vcov(slx)[names(b1), names(b1) ]
  V2 <- vcov(sdem)[names(b2), names(b2) ]
  dV <- V2 - V1

  tibble(
    Hstat = t(db) %*% MASS::ginv(dV) %*% db, 
    "p-value" = pchisq(Hstat, df = Matrix::rankMatrix(dV), lower.tail = FALSE)
  )
}

slx_sdem_htest <- slx_hausman(slx_vs_sdem[[1]], slx_vs_sdem[[2]])
```

To determine which spatial effects specification was appropriate, we estimated
SLX and SDEM models of physical activity participation rates as a function of
tract covariates and  accessibility. These two models are presented in Table 
\ref{tab:slx-sdem}. With only a few exceptions, the SLX and SDEM coefficient
estimates for corresponding covariates lie within the 95\% confidence intervals
of the other model. A Hausman-style test [@LeSage2008] on the coefficients 
assumes a null hypothesis that the coefficients are equivalent; this test 
produces $p$-value of only $`r slx_sdem_htest[2]`$. Though this statistic is
technically beneath a common hypothesis test threshold of $\alpha = 0.05$, we
fail to reject the null hypothesis that the coefficients are equivalent, as 
the differences are not practically different from each other. The consequences
of rejecting the null hypothesis in this case would be to suggest a model with 
spatial dependence of the dependent variable; as stated above, we feel that such
a relationship is unreasonable. As a consequence of these analyses, we adopt the
SDEM specification moving forward as the spatial lag of the errors is 
significant and the overal log likelihood of the SDEM is higher than the SLX 
specification.

```{r slx-sdem, results = "asis"}
texreg(slx_vs_sdem, single.row = TRUE, ci.force = TRUE, 
       custom.coef.names = c(names_for_terms, "Accessibility", lambda), 
       # Goodness of fit (LM and SP are different)
       custom.gof.rows = list(
         "Log Likelihood" = lapply(slx_vs_sdem, logLik) %>% unlist(),
         "Num. Obs." = lapply(slx_vs_sdem, function(s) length(s$residuals))
       ),
       include.rsquared = F, include.adjrs = F, include.aic = F, include.loglik = F,
       include.parameters = F, include.nobs = F,
       use.packages = FALSE, booktabs = TRUE,
       caption = "Comparison of SLX and SDEM Coefficients",
       caption.above = TRUE)
```
